---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The `rcdf` Package

<!-- badges: start -->
<!-- badges: end -->

`rcdf` provides functions to easily create, read, and manipulate RCDF files (encrypted Parquet format) in R. The package supports robust encryption and decryption workflows, integrates with Arrow for efficient data access, and provides utilities for managing metadata, generating AES keys, and more.

Key features include:

- **Secure Data Handling**: Functions for reading and writing encrypted Parquet files using AES and RSA encryption.
- **Metadata Management**: Tools for handling and storing metadata in RCDF files, including automated key generation and decryption.
- **Parquet Integration**: Full integration with the `arrow` package to read and write Parquet files seamlessly.
- **Cross-Platform Support**: Compatible with Linux, macOS, and Windows environments.

## Installation

You can install the development version of rcdf from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("yng-me/rcdf")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rcdf)
## basic example code
```



