---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The `rcdf` Package

<!-- badges: start -->
[![R-CMD-check](https://github.com/yng-me/rcdf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/yng-me/rcdf/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/rcdf)](https://CRAN.R-project.org/package=rcdf)
<!-- badges: end -->

The `rcdf` package is a comprehensive toolkit for securely working with RCDF (encrypted Parquet) files in R. RCDF is a custom data format designed to provide strong encryption and metadata management for sensitive datasets. With `rcdf`, users can easily handle encrypted data, including reading, writing, and exporting data stored in this secure format.

Key features include:

- **Secure data handling**: Functions for reading and writing encrypted Parquet files using AES and RSA encryption.
- **Metadata management**: Tools for handling and storing metadata in RCDF files, including automated key generation and decryption.
- **Parquet integration**: Full integration with the `arrow` package to read and write Parquet files seamlessly.
- **Cross-platform support**: Compatible with Linux, macOS, and Windows environments.

## Installation

Install from CRAN with:

```{r, eval=FALSE}
install.packages("rcdf")
```


You can also install the development version of `rcdf` from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("yng-me/rcdf")
```

Once installed, you can load the package and start working with RCDF files.

```{r, eval=FALSE}
library(rcdf)
```
